---
title: ""
name: "Lisa Anders"
---

## Countries I've been to

--- 

```{r}



#https://www.statsandr.com/blog/world-map-of-visited-countries-in-r/
```


## What are you looking for? {.tabset}

---

### Hiking

<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1Mv6AeXfYMUqa4GM-h4n_04P07Z07AoLt" width="640" height="480"></iframe>

--- 

### Food

<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1uUYvwjkox7eGdAuLrPNmmBMfx_oRsuq6" width="640" height="480"></iframe>

--- 

### Roadside Attractions 

<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1dqtzkAyIi666_2zloAvTcc2B8PRFt95u" width="640" height="480"></iframe>

--- 

### Tours (AKA "How It's Made")

<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1JgbWPMd5iMfrAe92mAiLLAKcktkBSfPw" width="640" height="480"></iframe>

--- 

### Music Venues

<iframe src="https://www.google.com/maps/d/u/0/embed?mid=1naGG2y-HejDrxXwb5JVVeg1K-XWOu-9Z" width="640" height="480"></iframe>

--- 

## Notes

This was possible by using [Google Takeout](https://takeout.google.com/settings/takeout) to export my saved places from [Google Maps](https://www.google.com/maps/) and import them into [Google My Maps](https://www.google.com/maps/d/u/0/?dg=feature). From there I was able to create a map, enable it to be public, and get the embed info for embedding into this webpage. 

Reference: https://support.google.com/maps/thread/5149639?hl=en (huge thanks to user Facu Pola for finding the slightly hidden option for downloading saved places!)



```{r eval=FALSE,echo=FALSE}

# https://stackoverflow.com/questions/17087479/get-a-list-of-font-awesome-icons 

#default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti.
#Don't like: sandstone (dark header), cerulean(very blue), readable(almost but don't like blue text),yeti (dark header), flatly (dark header), darkly (blueheader but dark theme), united (red), cosmo (black header)
#Very nice: paper, journal (can't put my finger on it but it is kinda goofy), simplex (but took longest to load), spacelab (has light grey header),lumen (light header)

library(json)


```

